---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Installation

```{r eval=FALSE}
library(devtools)
install_github("ChandlerLutz/VARfunctions")
```

```{r }
library(VARfunctions)
```

## Load the Data

Load the data directly from the package
```{r }
data(us.macro.data)
#Industrial Production, CPI less food and energy,
#and the Fed funds rate downloaded from the FRED
#(see below for how the data was downloaed)
head(us.macro.data)
```

The data is an xts object
```{r }
is.xts(us.macro.data)
```

# Local Projection Impulse Response

The `lp_irf()` function returns the local projection impulse response
of Jorda (2005) for forecast horizon `h` and `max.lags` max lags
```{r }
lp_irf(us.macro.data, h = 1, max.lags = 14)
```
The functions returns the IRFs for each variable following a reduced
form disturbance in every other variable. Reading the bottom row for
`FEDFUNDS.1`, we can see that a 1 unit (1 percentage point increase)
in the fed funds rate is associated with a 0.016 percent increase in
industrial production, a 0.025 percent increase in the inflation rate,
a -0.0077 percentage point decline in the unemployment rate, and a 1.3
percentage point increase in the fed funds rate the next month.

## Local Projection Impulse Response h = 1,...,12

```{r }
LP.irfs.out <- lapply(1:12, function(h) {
    lp_irf(y = us.macro.data, h = h,
           max.lags = 14)
})
LP.irfs.out <- do.call("rbind", LP.irfs.out)
head(LP.irfs.out)
```

## Local Projection IRFs for just the fed funds rate

```{r }
LP.irfs.out[grepl("FEDFUNDS", rownames(LP.irfs.out)), ]
```


## How the data was downloaded

The following code shows how to download the package data

```{r eval=FALSE}
#Load packages
library(quantmod)
#Time Series that we want to download
#Note: ORDER MATTERS for structural identification
#Industrial Production, CPI less food and energy,
#and the Fed funds rate
ts <- c("INDPRO", "CPILFESL", "UNRATE", "FEDFUNDS")
getSymbols(ts, src="FRED")
#Log first difference of industrial production
INDPRO <- na.omit(diff(log(INDPRO)) * 100)
#Log first difference of CPI
CPILFESL <- na.omit(diff(log(CPILFESL)) * 100)
#Merge all of the time series
us.macro.data <- INDPRO
for (i in 2:length(ts))
    us.macro.data <- na.omit(merge(us.macro.data, get(ts[i])))
us.macro.data <- us.macro.data["/2008-01-01"] ##Up to 2008-01-01
```
